A Large-Scale 3D Object Recognition dataset

### 2016-06-30 paper.tex
Related

         \begin{tabular}{p{4.2cm} p{0.3cm} p{1.2cm} p{1.5cm} p{1.55cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm}}

@@

\section{Related work} \label{sec:related_work}

@@

The last 10 years a few 3D object recognition datasets have been published. Mainly in conjunction with algorithms for local feature description \cite{Mian2006},\cite{Taati2007},\cite{Taati2011},\cite{Tombari2010},\cite{Salti2014}, correspondence matching and rejection \cite{Rodola2013}, pose hypothesis verification \cite{Aldoma2012} and 3D keypoint detection \cite{Mian2010}. Common for all existing dataset are the limited number of 3D object models and scenes. A comparison of the different datasets are presented in Table \ref{tab:datasets}. The most common used datasets are the UWA  \cite{Mian2006}, \cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2011} and the Bologna \cite{Salti2014}, \cite{Tombari2010}. These datasets are widely used in performance evaluations of  local feature descriptors \cite{Guo2015}, \cite{Buch2016}, keypoint detectors \cite{Salti2011} and surveys \cite{Guo2014}, \cite{FilipeAlexandre2014}. The main problem of all the datasets are; size, variety of objects and occlusion/clutter estimates. The recent comparison studies \cite{Guo2015}, \cite{Buch2016} revival that the data for evaluation are not good enough to scientific distinguish results. The studies exactly showed that one local feature descriptor preformed very good for one dataset but fail in other datasets. The reason could be twofold; the local feature descriptors are not generalizing well and/or the evaluation data is too limited. This work tries to answer this question.\\

\textbf{Local feature descriptors:}\\
{\color{red} AGB will you write this. Length around 1 colum}
During the last three decade, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3D Shape Contex (3DSC) \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensor \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, Unique shape context (USC) \cite{usc2010}, Point Feature Histogram (PFH)\cite{Rusu2008}, Fast Point Feature Histogram (FPFH) \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015}, Tri-Spin-Image (TriSI)\cite{Guo2015}. The descriptors find usages in applications such as 3D object categorization, recognition, retrial, analysis, registration and reconstruction among others. Designing descriptors which are distinctive and robust to occlusion and noise are still and ongoing research topic. Recent studies has shown that the proposed features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}. The studies proved one of the main issue in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well in many different object classes, e.g. flat, rotational symmetrical and geometrical feature rich objects. What feature(s) to use are still dependant of the object geometry. These studies poses a relevant research question, are the local feature descriptors not descriptiveness enough to generalize over different object classes or are the evaluation data to limited? The evaluation dataset there are used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016}, consists mainly of objects with many descriptive and distinctive geometrical features. In this work we try to answer this fundamental question by creating the data foundation to evaluate the performance of each local feature descriptors by applying statistic.

Local feature descriptor aims at computing a distinctive and robust N-dimensional feature vector around a point, by considering the k-neighbour points in euclidean space. The radius of the K-Nearest Neighbour search (KNN), the support radius is often one of the critical parameters in the pipeline. Local feature descriptors are often split into tow different categories, spatial and geometrical histograms \cite{Guo2015}. Global feature descriptors, typical computes a descriptors by considering the spatial and/or geometrical relations between two or more local feature descriptors on a 3D geometry.

Local shape features can be split into two different categories, spatial and geometrical histograms \cite{Guo2015}. 
Early work by Stein and Medioni \cite{Stein1992} used a combination of edges and small surfaces patches for 3D matching in range images. Later Johnson  and Albert introduced Spin Images \cite{Johnson1999}

Spin Images \cite{Johnson1999}\\
Froome \etal \cite{Frome2004} presented a local descriptor 3D shape context.
%USC \cite{usc2010}\\

%PFH \cite{Rusu2008}
%FPFH \cite{Fpfh2009}\\
%ECSAD \cite{Ecsad2015}\\
%ROPS \cite{Guo2013}\\
%SHOT \cite{Salti2014}\\
%NDHIST\\
%PPF \cite{Drost2010}\\
%SHOT \cite{Tombari2010}\\

Recently, a couple of benchmarks of local feature descriptors has been presented. Guo \etal \cite{Guo2015} presented a comprehensive comparison of most common local feature descriptors. The 
Feature Fusion \cite{Buch2016}\\
Feature comparision Yulan et.al. \cite{Guo2015}

>>>>

         \begin{tabular}{p{3.5cm} p{0.3cm} p{1.2cm} p{1.5cm} p{1.55cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm} p{0.3cm}}

@@

\section{Related work}\label{sec:related_work}

@@

The last 10 years a few 3D object recognition datasets have been published. Mainly in conjunction with algorithms for local feature description \cite{Mian2006},\cite{Taati2007},\cite{Taati2011},\cite{Tombari2010},\cite{Salti2014}, correspondence matching and rejection \cite{Rodola2013}, pose hypothesis verification \cite{Aldoma2012} and 3D keypoint detection \cite{Mian2010}. Common for all existing dataset are the limited number of 3D object models and scenes. A comparison of the different datasets are presented in Table \ref{tab:datasets}. The most common used datasets are the UWA  \cite{Mian2006}, \cite{Mian2010}, Queens \cite{Taati2007},\cite{Taati2011} and the Bologna \cite{Salti2014}, \cite{Tombari2010}. These datasets are widely used in performance evaluations of  local feature descriptors \cite{Guo2015}, \cite{Buch2016}, keypoint detectors \cite{Salti2011} and surveys \cite{Guo2014}, \cite{FilipeAlexandre2014}. The main problem of all the datasets are; size, variety of objects and occlusion/clutter estimates. The recent comparison studies \cite{Guo2015}, \cite{Buch2016} revival that the data for evaluation are not good enough to scientific distinguish results. The studies exactly showed that one local feature descriptor preformed very good for one dataset but fail in other datasets. The reason could be twofold; the local feature descriptors are not generalizing well and/or the evaluation data is too limited. This work tries to answer this question. {\color{blue} Unclear last sentence. How?}\\

\textbf{Local feature descriptors:}\\
{\color{red} AGB will you write this. Length around 1 colum} {\color{blue} Done.}
During the last three decades, a vast number of different 3D local feature descriptors have been proposed including SPLASH \cite{Stein1992}, Spin Image (SI) \cite{Johnson1999}, 3D Shape Context (3DSC) \cite{Frome2004}, LSP \cite{ChenBhanu2004}, 3D Tensors \cite{Mian2006}, THRIFT \cite{Flint2007}, MESH-HOG \cite{Zaharescu2009}, ISS \cite{Zhong2009}, Unique shape context (USC) \cite{usc2010}, Point Feature Histogram (PFH) \cite{Rusu2008}, Fast Point Feature Histograms (FPFH) \cite{Fpfh2009}, SHOT \cite{Tombari2010}, ROPS \cite{Guo2013}, ECSAD \cite{Ecsad2015} and Tri-Spin-Image (TriSI)\cite{Guo2015}. The descriptors find usages in applications such as 3D object categorization, recognition, retrieval, analysis, registration and reconstruction among others. Designing descriptors which are distinctive and robust to occlusion and noise is still an ongoing research topic. Recent studies has shown that the proposed features are not generalizing well over many types of geometry classes, \cite{Guo2015},\cite{Buch2016}. The studies proved one of the main issue in 3D object recognition today, namely the fact that there exist no local shape feature that describes the geometry well over many different object classes, e.g. flat, rotational symmetrical and geometrically feature rich objects. What feature(s) to use are still dependent on the object geometry. These studies pose a relevant research question, are the local feature descriptors not descriptiveness enough to generalize over different object classes or are the data used for evaluation too limited? The evaluation datasets used for the evaluation in general and in \cite{Guo2015},\cite{Buch2016} consist mainly of objects with many descriptive and distinctive geometrical features. In this work we try to answer this fundamental question by creating a better data foundation and by evaluating the performance of each local feature descriptors by applying statistical analyses.
{\color{blue} TS This last sentence I believe is not relevant anymore, since the statistical analysis are postponed?}

Local feature descriptors aim at computing a distinctive and robust N-dimensional feature vector around a point, by considering the points in an Euclidean neighborhood. The support radius determining the size of the neighborhood is often one of the critical parameters in the pipeline. Local feature descriptors are often split into two different categories, spatial and geometrical histograms \cite{Salti2014}. Global feature descriptors, typical computes a descriptors by considering the spatial and/or geometrical relations between two or more local feature descriptors on a 3D geometry. {\color{blue} TS I would remove the last sentence about global descriptors.}
